### 2019-06-30 papers/journal/fig3.tex
Update on the fig 2 legend

	 \end{tikzpicture}
	 \caption{Output complete VTS} 
	 \label{fig:synth-vts2}
  \end{subfigure}%
  \caption{An example of synthesis of edge and molecules in the partial VTS} \label{fig:synth-vts}
\end{figure}

>>>>

	 \end{tikzpicture}
	 \caption{Output complete VTS} 
	 \label{fig:synth-vts2}
  \end{subfigure}%
  \caption{An example of the synthesis of edge and molecules in the partial VTS. Black edges correspond to the edges in the input VTS and the synthesized edge is shown in the red color. Similarly, synthesized molecules are shown in blue color.} \label{fig:synth-vts}
\end{figure}
